Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-26 datapaper_baseline.tex
Edit-Over-Paper-One-Pass

To facilitate future research on this database, we apply our automatic multi-leaf segmentation, alignment, and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis imagery to provide a baseline.
Specifically, we apply it on fluorescence and RGB modalities. 
Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis.
Therefore, it will not be applied to bean plant as it does not belong to rosette plants.
%In addition, we also apply it on the RGB modality and use the propagated labels for evaluation.

\subsection{Multi-leaf Segmentation and Tracking Framework}
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
We treat all images in $9$ days as a video from first image on the first day to the last image on the last day.
To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
The scales for fluorescence images and RGB images are different due to the different image resolutions. 
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates.

Our work is motivated by Chamfer Matching (CM) technique~\cite{barrow1977parametric}, which is used to align two edge maps.
We extend it to simultaneously align multiple overlapping objects.
For plant segmentation, we use simple thresholding process and edge detection to generate an image mask and edge map.
The best threshold is learnt from the training set, which is done by tuning the threshold in a certain range and find the best one by evaluating the overlap of the segmented masks with the groundtruth label masks.
The edge map and mask are used in the alignment and tracking optimization.

First, we find the best location of each template in the edge map that has the minimal CM distance, which will result in an over-completed set of leaf candidates.
Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.

In the tracking process, we delete a leaf when it becomes too small.
We develop a procedure to generate new leaves when there is a relatively large portion of the mask has not been covered by current leaf candidates.
For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
The labeled color for each leaf in the video remains the same during the tracking process.

@@

\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/9_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/10_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/11_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/12_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/14_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/15_2}\\
(a) & (b) & (c) & (d) & (e) & (f) \\
\end{tabular}
\caption{Leaf alignment results on the last frame of $6$ fluorescence Arabidopsis videos. First row shows the original images. Second row shows the alignment results with red points denoting the boundary of the leaf templates in the blue bounding boxes. The numbers on the leaves are the leaf IDs representing the order of the leaf being selected and they will be consistent during tracking.}
\label{fig:alignResult}
\end{centering}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=.81\textwidth]{Figures/performance.pdf}\\
\caption{Performance of the baseline method on the testing set of the fluorescence modality of Arabidopsis plant.}
\label{fig:performance}
\end{figure*}

\subsection{Performance and Analysis}
We apply our algorithm to all $135$ frames of each video and evaluate the performance on labeled $36$ frames.
Figure~\ref{fig:alignResult} shows some examples of leaf alignment results on the last frame of each video. 
Our framework works very well on segmenting large leaves with no overlap to neighbor leaves.
For overlapping leaves, it becomes more challenging as the edges in the overlapping area are more difficult to be detected.
However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(c)$ of Figure~\ref{fig:alignResult}.
When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(a), (d), (e)$ of Figure~\ref{fig:alignResult}.

%Leaf alignment provides the leaf candidates for tracking over time.
Figure~\ref{fig:trackExample} shows the leaf tracking result of one Arabidopsis video in both fluorescence and RGB modalities. 
We can see the high quality leaf label propagation results on this video. 
The leaf template transformation works well for most of the leaves.
As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
As shown in Figure~\ref{fig:trackExample} (b)(e), purple leaf replaces the red leaf at day $6$.
%Our backward tracking algorithm tracks leaves from the last frame to the first frame.
The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$ (Figure~\ref{fig:trackExample}(c)).
Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample}(c)).
However, they are still evaluated as well aligned and segmented leaves.
\todo{May add more if the final figure updated}

For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure~\ref{fig:performance}.
For both RGB and fluorescence modalities, {\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
As $\tau$ keeps increasing, {\it{ULR}} approaches a constant value, which is the different number in leaf counting that results from both miss detection and false alarms.
{\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging.
{\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves.
Note that {\it{TC}} is influenced by the length of frames evaluated for each video.
As the longer frames we evaluate, the higher chance tracking will fail.
Overall, our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors.

@@

>>>>

To facilitate future research on this database, we apply our automatic multi-leaf segmentation, alignment, and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis imagery to provide a baseline.
Specifically, we apply it on fluorescence and RGB modalities. 
Our work is motivated by Chamfer Matching (CM) technique~\cite{barrow1977parametric}, which is used to align two edge maps.
We extend it to simultaneously align multiple overlapping objects.

Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis.
Therefore, it will not be applied to bean imagery as it does not belong to rosette plant.
%In addition, we also apply it on the RGB modality and use the propagated labels for evaluation.

\subsection{Multi-leaf Segmentation and Tracking Framework}
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
We treat all images in $9$ days as a video from first image on the first day to the last image on the last day.
To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
The scales for fluorescence images and RGB images are different due to the different image resolutions. 
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates for each modality.

For plant segmentation, we use simple thresholding process and edge detection to generate an image mask and edge map.
The best threshold is learnt from the training set, which is done by tuning the threshold in a certain range and find the best one by evaluating the overlap of the segmented masks with the groundtruth label masks.
The edge map and mask are used in the alignment and tracking optimization.

First, we find the best location of each template in the edge map that has the minimal CM distance, which will result in an over-completed set of leaf candidates from all templates.
Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations, and boundary of each leaf.
Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.

In the tracking process, we delete a leaf when it becomes too small.
A new leaf is generated when there is a relatively large portion of the mask that has not been covered by current leaf candidates.
For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
The labeled color for each leaf in the video remains the same during the tracking process.

@@

\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/9_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/10_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/11_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/12_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/14_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/15_2}\\
(a) & (b) & (c) & (d) & (e) & (f) \\
\end{tabular}
\caption{Leaf alignment results on the last frame of $6$ fluorescence Arabidopsis videos. First row shows the original images. Second row shows the alignment results with red points denoting the boundaries of the leaf templates in the blue bounding boxes. The numbers on the leaves are the leaf IDs representing the order of the leaf being selected and will be consistent during tracking.}
\label{fig:alignResult}
\end{centering}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[trim= 10 0 0 10, clip, width=.81\textwidth]{Figures/performance_fmp_rgb.pdf}\\
\caption{Performance of the baseline method on the testing set of the fluorescence and RGB modalities of Arabidopsis plant.}
\label{fig:performance}
\end{figure*}

\subsection{Performance and Analysis}
We apply our algorithm to all frames of each video and evaluate the performance on labeled frames.
Figure~\ref{fig:alignResult} shows some examples of leaf alignment results on the last frame of each video. 
Our framework works very well on segmenting large leaves with no overlap to neighbor leaves.
For overlapping leaves, it becomes more challenging as the edges in the overlapping area are more difficult to be detected.
However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in Figure~\ref{fig:alignResult} $(c)$.
When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in Figure~\ref{fig:alignResult} $(a), (d), (e)$.

%Leaf alignment provides the leaf candidates for tracking over time.
Figure~\ref{fig:trackExample} shows the leaf tracking result of one Arabidopsis video in both fluorescence and RGB modalities. 
We can see the high quality leaf label propagation results on this video. 
The leaf template transformation works well for most of the leaves.
As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
As shown in Figure~\ref{fig:trackExample} (b),(e), purple leaf replaces the red leaf at day $6$.
%Our backward tracking algorithm tracks leaves from the last frame to the first frame.
The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$ (Figure~\ref{fig:trackExample} (c)).
Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample} (c)).
However, they are still evaluated as well aligned and segmented leaves.

For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure~\ref{fig:performance}.
For both RGB and fluorescence modalities, {\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
As $\tau$ keeps increasing, {\it{ULR}} approaches a constant value, which is the different number in leaf counting that results from both miss detection and false alarms.
{\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging.
{\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves.
Note that {\it{TC}} is influenced by the length of frames evaluated for each video.
As the longer frames we evaluate, the higher chance tracking will fail.
Our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors on fluorescence images.

@@

Overall, the performance on fluorescence images is better than the performance on RGB images.
This is due to two reasons. 
First, the resolution of RGB images is much lower than that of fluorescence images, which will results in the miss detection of small leaves, and more severe leaf occlusions. 
Second, the label propagation causes some error, which is inevitable with the label homography-based mapping.

### 2015-07-26 datapaper_calibration.tex
Edit-Over-Paper-One-Pass

A planar checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.
While the grid pattern is not visible in the depth image, it is nevertheless observed in the reflected IR image whose pixels correspond to the depth pixels.
This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera.
In this process the poses of all three cameras are also calculated relative to the checkerboard.
The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Fig.~\ref{fig:CameraConfiguration}.

@@

The depth noise $\varepsilon$ is modeled as the sum of an image dependent term $\varepsilon_I$ and a sensor dependent term $\varepsilon_S$:
\begin{equation}
\varepsilon = \varepsilon_I + \varepsilon_S. \label{eq:epsilon}
\end{equation}
The term $\varepsilon_I$ is a random variable for each pixel with a value that varies between subsequent images taken from a fixed pose of a static scene.
On the other hand, $\varepsilon_S$ is a random variable for each pixel that models its depth offset, and its value only changes when the scene changes.
The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images.
Object depth, $d$, has a large impact on $\varepsilon_I$.
For constant depth, we observed that the primary factor affecting the variance is the pixel radius $r$, from the image center.
Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.
Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.
From our experiments we build up a lookup table for this as plotted in Fig.~\ref{fig:Noise}.

\begin{table*}[t!]
\begin{center}
\caption{Summary of Arabidopsis and Bean databases.}
\label{tab:stat}
\begin{tabular}{c|c|c|c|c|c}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Plants & Subjects & Days & Images/Day & Total Images & Annotated Images \\
\hline
Arabidopsis & $16$ & $9$ & $15$ & $2,160\times 4$ & $576\times 4$ \\
\hline
Bean & $5$ & $5$ & $14$ & $350\times 4$ & $175\times 2$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

Averaging over repeated images of a scene will not remove all the depth error as there are pixel depth offsets that are constant for images of the same scene.
We model these with $\varepsilon_S$.
To estimate its standard deviation $\sigma_S$, we first average over many depth measurement images, in our case $300$, to obtain pixel depth estimates that approximately eliminate the effect of $\varepsilon_I$. Then by calculating true ray depths on a known surface, in our case the observed plane, and further assuming that $\varepsilon_S$ has the same standard deviation for all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths. In our experiments we obtained $\sigma_S=6.5mm$ and found that it was insensitive to changes in depth.

@@

There are additional sources of noise not modeled by this.
Object albedo has an impact although this is fairly weak for strong signal reflections.
Factors with large impact on signal noise include: object specularities, sharp variations in object albedo, mixed-depth pixels on object edges, and cases of very-low signal reflection, all of which can lead to very large variances.
One of the utilities of having a model for variance is that it can be compared with the measured variance, and the difference used as a cue for portions of the scene that violate our modeling assumptions.

>>>>

A planar checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.
While the grid pattern is not visible in the depth image, it is nevertheless observed in the reflected IR image whose pixels correspond to the depth pixels.
This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera.
In this process the poses of all three cameras are also calculated relative to the checkerboard.
The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as shown in Figure~\ref{fig:CameraConfiguration}.

@@

The depth noise $\varepsilon$ is modeled as the sum of an image dependent term $\varepsilon_I$ and a sensor dependent term $\varepsilon_S$:
\begin{equation}
\varepsilon = \varepsilon_I + \varepsilon_S. \label{eq:epsilon}
\end{equation}
The term $\varepsilon_I$ is a random variable for each pixel with a value that varies between subsequent images taken from a fixed pose of a static scene.
On the other hand, $\varepsilon_S$ is a random variable for each pixel that models its depth offset, and its value only changes when the scene changes.
The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
In our experiments we observed a flat, uniform albedo surface (\todo{Danial: Please define ``albedo" here as from Comment $38$}) perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images.
Object depth, $d$, has a large impact on $\varepsilon_I$.
For constant depth, we observed that the primary factor affecting the variance is the pixel radius $r$, from the image center.
Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.
Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.
From our experiments we build up a lookup table for this as plotted in Figure~\ref{fig:Noise}.

\begin{table*}[t!]
\begin{center}
\caption{Summary of Arabidopsis and Bean databases. The ``$\times n$" represents the number of modalities.}
\label{tab:stat}
\begin{tabular}{c|c|c|c|c|c}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Plants & Subjects & Days & Images/Day & Total Images & Annotated Images \\
\hline
Arabidopsis & $16$ & $9$ & $15$ & $2,160\times 4$ & $576\times 4$ \\
\hline
Bean & $5$ & $5$ & $13$ & $325\times 4$ & $175\times 2$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

Averaging over repeated images of a scene will not remove all the depth error as there are pixel depth offsets that are constant for images of the same scene.
We model these with $\varepsilon_S$.
To estimate its standard deviation $\sigma_S$, we first average over many depth measurement images, in our case $300$, to obtain pixel depth estimations that approximately eliminate the effect of $\varepsilon_I$. Then by calculating true ray depths on a known surface, in our case the observed plane, and further assuming that $\varepsilon_S$ has the same standard deviation for all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths. In our experiments we obtained $\sigma_S=6.5~mm$ and found that it was insensitive to changes in depth.

@@

There are additional sources of noise that are not modeled by this.
Object albedo has an impact although this is fairly weak for strong signal reflections.
Factors with large impact on signal noise include: object specularities, sharp variations in object albedo, mixed-depth pixels on object edges, and cases of very-low signal reflection, all of which can lead to very large variances.
One of the utilities of having a model for variance is that it can be compared with the measured variance, and the difference used as a cue for portions of the scene that violate our modeling assumptions.

### 2015-07-26 datapaper_hardware.tex
Edit-Over-Paper-One-Pass

\subsection{Hardware Setup}

In this section, we introduce the hardware used for capturing fluorescence, IR, RGB color, and depth imagery data for both plants.
Figure~\ref{fig:hardware} illustrates the hardware and imaging setup used in our data collection.

\subsubsection{Fluorescence and IR Images}
Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
%
Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
Since $940nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800nm$) in the region where we do IR reflectance ($940nm$)~\cite{butler1964actton}.
%
Note that the other modalities were captured only at day time, so that they will not interfere plant growth.

@@

\subsubsection{RGB Color and Depth Images} %This section describes characterizes the data from this sensor, particularly the depth data.

The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}. 
The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
The depth sensor uses a flash near IR illuminator and measures the time-of-flight~\cite{Hansard2013} of the beam at each pixel to obtain depth estimates along with an IR reflectance at each pixel.

There is a number of limitations to the depth sensor that becomes the sources of depth errors.
The primary measurement limitation on the range-to-target is the strength of the reflected beam.
As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30cm$.
Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
In addition reflective surfaces at grazing angles are less reliably measured since little signal is reflected.
Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.  
Thus the depth pixels that are most reliable and are of most use are those that fall on plant foliage.

% For one-column wide figures use
\begin{figure}
\begin{tabular}{c}
  \includegraphics[width=\linewidth,trim=120 240 80 300,clip]{Figures/CameraConfiguration} \\
  ($a$)\\
  \includegraphics[width=0.65\linewidth,trim=175 220 162 180, clip,angle=-90,origin=c]{Figures/DepthOnBeanRGB} \vspace{-10mm} \\
  ($b$)\\
\end{tabular}
\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in $mm$, and distance to the target bean plant is roughly 620$mm$ in this example.  The image planes are plotted at depths proportional to the focal lengths.  The optical center of the color camera (left-most) defines the world coordinate system.  Close to it is the depth camera having much lower resolution.  The right-most camera is the combined fluorescent and IR camera. ($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.  This shows the projection into the color image (with $90^{\circ}$ rotation for economical use of space).  Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.  An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
\label{fig:CameraConfiguration}
\end{figure}

\subsubsection{Image collection}
The imagery data, including fluorescence, IR reflectance,  RGB color, and the $3$D depth images, is collected once every hour.
%
Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and IR reflectance images collected sequentially at $2$-minute interval by the IR filtered CCD camera.
%
No substantial movements or growth were observed within the about four-minute period required for image capture using all four modalities, minimizing potential problems in image calibration.

>>>>

\subsection{Hardware Setup}
In this section, we introduce the hardware used for capturing fluorescence, IR, RGB color, and depth imagery data for both plants.
Figure~\ref{fig:hardware} illustrates the hardware and imaging setup used in our data collection.

\subsubsection{Fluorescence and IR Images}
Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
A set of $5$ images were captured using a Hitachi KP-F$145$GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
Note that the other modalities were captured only at day time, so that they will not interfere plant growth.

@@

\subsubsection{RGB Color and Depth Images} %This section describes characterizes the data from this sensor, particularly the depth data.
The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}.
The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
The depth sensor uses a flash near IR illuminator and measures the time-of-flight~\cite{Hansard2013} of the beam at each pixel to obtain depth estimates along with an IR reflectance at each pixel.

There is a number of limitations to the depth sensor that becomes the sources of depth errors.
The primary measurement limitation on the range-to-target is the strength of the reflected beam.
As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30~cm$.
Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
In addition reflective surfaces at grazing angles are less reliably measured since little signal is reflected.
Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.
Thus the depth pixels that are most reliable and are of most use are those that fall on plant foliage.

% For one-column wide figures use
\begin{figure}
\begin{tabular}{c}
  \includegraphics[width=\linewidth,trim=120 240 80 300,clip]{Figures/CameraConfiguration} \\
  ($a$)\\
  \includegraphics[width=0.65\linewidth,trim=175 220 162 180, clip,angle=-90,origin=c]{Figures/DepthOnBeanRGB} \vspace{-10mm} \\
  ($b$)\\
\end{tabular}
\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in $mm$. The distance to the target bean plant is roughly $620~mm$ in this example.  The image planes are plotted at depths proportional to the focal lengths.  The optical center of the color camera (left-most) defines the world coordinate system.  Close to it is the depth camera having much lower resolution.  The right-most camera is the combined fluorescent and IR camera. ($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.  This shows the projection into the color image (with $90^{\circ}$ rotation for economical use of space).  Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.  An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
\label{fig:CameraConfiguration}
\end{figure}

\subsubsection{Image collection}
The imagery data, including fluorescence, IR reflectance,  RGB color, and the $3$D depth images, is collected once every hour.
Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and IR reflectance images collected sequentially at $2$-minute interval by the IR filtered CCD camera.
No substantial movements or growth were observed within the about $4$-minute period required for image capture using all four modalities, which minimize the potential problems in image calibration.
